Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-04-15 paper/main.tex
Revise system model

The rest of this paper is organized as follows TODO
%

@@

In our work, we propose a reservoir computing based prediction framework, which predicts the new precoders by tapping the temporal correlations captured from past observed precoders ($f_P$).
We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}, however, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
Previous work \cite{Gupt1905:Predictive,6891198} have $f_P$ and $q_P$ independent of each other.
The detailed discussion on reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}. Finally, Section \ref{section5} concludes and presents future lines of work.

>>>>

@@

In our work, we propose a reservoir computing based prediction framework that predicts the new precoders by utilizing  temporal correlations that are captured from past observed precoders ($f_P$).
We reuse the $q_P$ algorithm from \cite{Gupt1905:Predictive,6891198}.
However, by incorporating the $q_P$ in the prediction framework, as discussed in subsequent sections, the $f_P$ function also exploits correlations in $q_P$ (codebook locality correlations), along with temporal correlations.
Previous work \cite{Gupt1905:Predictive,6891198} has considered $f_P$ and $q_P$ to be independent of each other.
A detailed discussion on the reservoir computing based model for $f_P$ and $q_P$ is presented in Section \ref{section3}.
The proposed reservoir computing scheme is evaluated against the temporal predictive quantization scheme in \cite{6891198}, and the simulation results are discussed in Section \ref{section4}. Finally, Section \ref{section5} concludes and presents future lines of work.
